Large squeezing in multicomponent trapped Bose-Einstein condensates

### 2012-11-21 large_number_squeezing_with_atoms.tex
Add figure to paper
And add a preliminary caption so I don't forget the details

\section{Effects of trap geometries on squeezing in 1D}
\begin{itemize}
  \item Plot of squeezing for given set of params for gaussian, TF, constant density, show it get steadily better
\end{itemize}

>>>>

\section{Effects of trap geometries on squeezing in 1D}
\begin{itemize}
  \item Plot of squeezing for given set of params for gaussian, TF, constant density, show it get steadily better
\end{itemize}
This is shown in Figure~\ref{figModalSqueezingEffects1D}
\begin{figure}
    \centering
    \includegraphics[width=8cm]{figures/modal_squeezing_effects_1D.eps}
    \caption{Effects of mode shape on squeezing. The plot shows the normalized number variance in mode $\hat{a}$ as a function of the time the final coupling pulse is applied. Thick red line, analytic two-mode solution; solid blue line, constant density mode; dashed line, Thomas-Fermi mode; dash-dotted line, gaussian mode. The nonlinearities of the various 1D simulations have been adjusted for their mode shape so that they are equivalent to that of the 0D, two-mode mode nonlinearity. Parameters: $n_a = n_b =1 \times 10^5$, $\chi_{aa}=0.03 \hbar, \chi_{ab}=\chi_{bb}=0, \tau_{\mathrm{hold}}=3\times 10^{-4}$s, $\phi=4.0$. }
    \label{figModalSqueezingEffects1D}
\end{figure}
